Psychological Science Submission Letter

### 2023-03-27 paper/admin/cover_letter.tex
lots of bug fixes (no results are affected; all bugs were related to running the code in a fresh environment)

\title{Psychological Science Submission Letter}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[10pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac, animate, hyperref, pxfonts}

@@

\greetto{To the editors of \textit{Psychological Science}:}

@@

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Feature-based and
  location-based volitional covert attention affect memory at different timescales}, which we wish
to submit for publication as a Research Article in
\textit{Psychonomic Bulletin \& Review}.

Our manuscript reports two experiments that examine how feature-based
and location-based attention affect recognition memory.  We asked our
participants to view a series of composite (blended face-scene) image
pairs.  We instructed the participants to focus their attention to a
specific image category (face or scene) and location (left or right)
without moving their eyes from a central fixation point.  The two
experiments differed in how often we changed the attention cue.  We
found that the memory consequences of location-based attention were
measurable after just a single attention cue instruction
(5.5~seconds), and persisted for at least 2~minutes.  Our data suggest
that location-based attention enhances memory encoding at the attended
location.  By contrast, feature-based attention must be sustained for
an extended interval to substantially affect memory.  Our data suggest
that feature-based attention suppresses the encoding into memory of
unattended stimulus features.

>>>>

\documentclass[10pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac, animate, hyperref, pxfonts}

@@

\greetto{To the editors of \textit{Scientific Reports}:}

@@

\begin{document}
\begin{newlfm}

We have enclosed our manuscript entitled \textit{Category-based and
location-based volitional covert attention affect memory at different
timescales}, which we wish to submit for publication as an Article in
\textit{Scientific Reports}.

Our manuscript reports our findings from an experiment designed to study how
different aspects of covert attention affect memory. Our experiment comprised
two conditions that asked participants to \textit{sustain} or \textit{vary} the
focus of their covert attention, respectively, with respect to each of a series
of stimuli. Each stimulus comprised a pair of images (one on the left of the
screen and the other on the right), and each image comprised an equal blend of
a photograph of a face and a photograph of a scene. During each stimulus
presentation, we instructed participants to focus in on either the face or
scene component of either the left or right image \textit{without moving their
eyes}. (This is quite difficult to do naively, so we trained participants to do
this quickly and at will using a practice session prior to the main
experiment.) We used eye-tracking data to focus in on trials where participants
were specifically varying their focus of \textit{covert} attention (i.e., with
no change in where they were looking), as opposed to simply moving their eyes
to look at the to-be-attended images. We then administered recognition memory
tests that asked participants to rate the ``familiarity'' of attended,
unattended, and novel images.

As we anticipated, participants in both conditions remembered stimuli they
attended to better than unattended stimuli, and they rated both attended and
unattended stimuli they had seen as more ``familiar'' than novel images, during
a recognition memory test. We also found some interesting differences across
the two experimental conditions pertaining to how participants remembered
``partially attended'' stimuli. When participants varied the focus of their
attention more often, their memory was more influenced by location-based
attention (regardless of which image category they were attending). In
contrast, when participants sustained the focus of their attention over longer
intervals, their memory was more influenced by category-based attention
(regardless of which location they were attending). Our findings highlight a
dissociation between how location-based and category-based attention affect
memory encoding (and subsequent recognition). Location-based attention appears
to affect memory encoding on relatively short timescales by enhancing encoding
for stimuli at the attended location. On the other hand, category-based
attention appears to affect memory encoding on longer timescales by
\textit{suppressing} stimuli from the unattended category.
